---
title: "Geom Density 2d"
output: geom_density_2d
---
 https://ggplot2.tidyverse.org/reference/geom_density_2d.html

```{r}
source('cxplot.r')
library(ggplot2)
library(dplyr)
library(canvasXpress)
``` 

```{r}
cxplot(ggplot(faithful, aes(x = eruptions, y = waiting)) + geom_point() + xlim(0.5, 6) + ylim(40, 110) + geom_density_2d())
```

```{r}
cxplot(ggplot(faithful, aes(x = eruptions, y = waiting)) + geom_point() + xlim(0.5, 6) + ylim(40, 110) + geom_density_2d_filled(alpha = 0.5))
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + geom_density_2d(aes(colour = cut)))
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + geom_density_2d_filled() + facet_wrap(vars(cut)))
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + geom_density_2d_filled(contour_var = "ndensity") + facet_wrap(vars(cut)))
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + geom_density_2d_filled(contour_var = "count") + facet_wrap(vars(cut)))
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + stat_density_2d(geom = "raster", aes(fill = after_stat(density)), contour = FALSE) + scale_fill_viridis_c())
```

```{r}
set.seed(4393)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ]
cxplot(ggplot(dsmall, aes(x, y)) + stat_density_2d(geom = "point", aes(size = after_stat(density)), n = 20, contour = FALSE))
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

