---
title: "Geom Histogram"
author: "Isaac Neuhaus"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geom histogram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

 https://ggplot2.tidyverse.org/reference/geom_histogram.html

```{r}
library(ggplot2)
library(dplyr)
library(canvasXpress)
library(cxplot)
``` 

```{r}
cxplot(ggplot(diamonds, aes(carat)) + geom_histogram())
```

```{r}
cxplot(ggplot(diamonds, aes(carat)) + geom_histogram(binwidth = 0.01))
```

```{r}
cxplot(ggplot(diamonds, aes(carat)) + geom_histogram(bins = 200))
```

```{r}
cxplot(ggplot(diamonds, aes(price, fill = cut)) + geom_histogram(binwidth = 500))
```

```{r}
cxplot(ggplot(diamonds, aes(price, colour = cut)) + geom_freqpoly(binwidth = 500))
```

```{r}
cxplot(ggplot(diamonds, aes(price, after_stat(density), colour = cut)) + geom_freqpoly(binwidth = 500))
```

```{r}

```

```{r}

```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

