---
title: "Geom Bar"
author: "Isaac Neuhaus"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geom bar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

 https://ggplot2.tidyverse.org/reference/geom_bar.html

```{r}
library(ggplot2)
library(dplyr)
library(canvasXpress)
library(cxplot)
``` 

```{r}
cxplot(ggplot(mpg, aes(class)) + geom_bar())
```

```{r}
cxplot(ggplot(mpg, aes(class)) + geom_bar(aes(weight = displ)))
```

```{r}
cxplot(ggplot(mpg) + geom_bar(aes(y = class)))
```

```{r}
cxplot(ggplot(mpg, aes(class)) + geom_bar(aes(fill = drv)))
```

```{r}
df <- data.frame(trt = c("a", "b", "c"), outcome = c(2.3, 1.9, 3.2))
cxplot(ggplot(mpg, aes(y = class)) + geom_bar(aes(fill = drv), position = position_stack(reverse = TRUE)) + theme(legend.position = "top"))
```

```{r}
df <- data.frame(trt = c("a", "b", "c"), outcome = c(2.3, 1.9, 3.2))
cxplot(ggplot(df, aes(trt, outcome)) + geom_col())
```

```{r}
df <- data.frame(trt = c("a", "b", "c"), outcome = c(2.3, 1.9, 3.2))
cxplot(ggplot(df, aes(trt, outcome)) + geom_point())
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

