---
title: "Geom Violin"
author: "Isaac Neuhaus"
date: "`r Sys.Date()`"
output: 
    rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geom violin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

 https://ggplot2.tidyverse.org/reference/geom_violin.html

```{r}
library(ggplot2)
library(dplyr)
library(canvasXpress)
library(cxplot)
``` 

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin())
```

```{r}
cxplot(ggplot(mtcars, aes(mpg, factor(cyl))) + geom_violin())
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin() + geom_jitter(height = 0, width = 0.1))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(scale = "count"))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(scale = "width"))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(trim = FALSE))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(adjust = .5))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(aes(fill = cyl)))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(aes(fill = factor(cyl))))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(aes(fill = factor(vs))))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(aes(fill = factor(am))))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(fill = "grey80", colour = "#3366FF"))
```

```{r}
cxplot(ggplot(mtcars, aes(factor(cyl), mpg)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

