---
title: "Geom Density"
output: geom_density
---
 https://ggplot2.tidyverse.org/reference/geom_density.html

```{r}
source('cxplot.r')
library(ggplot2)
library(dplyr)
library(canvasXpress)
``` 

```{r}
cxplot(ggplot(diamonds, aes(carat)) + geom_density())
```

```{r}
cxplot(ggplot(diamonds, aes(carat)) + geom_density(adjust = 1/5))
```

```{r}
cxplot(ggplot(diamonds, aes(depth, colour = cut)) + geom_density())
```

```{r}
cxplot(ggplot(diamonds, aes(depth, fill = cut, colour = cut)) + geom_density(alpha = 0.1))
```

```{r}
cxplot(ggplot(diamonds, aes(carat, fill = cut)) + geom_density(position = "stack"))
```

```{r}
cxplot(ggplot(diamonds, aes(carat, after_stat(count), fill = cut)) + geom_density(position = "fill"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

