---
title: "Geom Rug"
output: geom_rug
---

 https://ggplot2.tidyverse.org/reference/geom_rug.html

```{r}
source('cxplot.r')
library(ggplot2)
library(dplyr)
library(canvasXpress)
``` 

```{r}
cxplot(ggplot(mtcars, aes(wt, mpg)) + geom_point() + geom_rug())
```

```{r}
cxplot(ggplot(mtcars, aes(wt, mpg)) + geom_point() + geom_rug(sides="b"))
```

```{r}
cxplot(ggplot(mtcars, aes(wt, mpg)) + geom_point() + geom_rug(sides="trbl"))
```

```{r}
cxplot(ggplot(mpg, aes(displ, cty)) + geom_point() + geom_rug())
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

