---
title: "Geom Contour"
output: geom_contour
---
 https://ggplot2.tidyverse.org/reference/geom_contour.html

```{r}
source('cxplot.r')
library(ggplot2)
library(dplyr)
library(canvasXpress)
``` 

```{r}
cxplot(ggplot(faithfuld, aes(waiting, eruptions, z = density)) + geom_contour())
```

```{r}
cxplot(ggplot(faithful, aes(waiting, eruptions)) + geom_density_2d())
```

```{r}
cxplot(ggplot(faithfuld, aes(waiting, eruptions, z = density)) + geom_contour_filled())
```

```{r}
cxplot(ggplot(faithfuld, aes(waiting, eruptions, z = density)) + geom_contour(bins = 5))
```

```{r}
cxplot(ggplot(faithfuld, aes(waiting, eruptions, z = density)) + geom_contour(binwidth = 0.001))
```

```{r}
cxplot(ggplot(faithfuld, aes(waiting, eruptions, z = density)) + geom_contour(colour = "red"))
```

```{r}
library(interp)
data(franke, package = "interp")
origdata <- as.data.frame(interp::franke.data(1, 1, franke))
grid <- with(origdata, interp::interp(x, y, z))
griddf <- subset(data.frame(x = rep(grid$x, nrow(grid$z)),
                            y = rep(grid$y, each = ncol(grid$z)),
                            z = as.numeric(grid$z)), !is.na(z))
  
cxplot(ggplot(griddf, aes(x, y, z = z)) + geom_contour_filled() + geom_point(data = origdata))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

